### 2020-12-21 03_problem.tex
Updates from Overleaf

\begin{figure}[h]
    % \vspace{-.3in}
	\centering
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    % \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    % \vspace{-.35in}
\end{figure}
Two robot arms \footnote{We shall use superscripts to denote arms, and subscripts to index into some sequence or data-structure dependent on context, unless stated otherwise.} $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of \revisions{$d$-dimensional} $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process. Let the set of collisions induced between the geometries of both the arms at two configurations along the path (at $t$) be denoted by the expression $ \pi^1(t) \ominus \pi^2(t) $. If there are no collisions then $\pi^1(t) \ominus \pi^2(t) = \emptyset$.
% Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. 
The space of dual-arm paths $\mathcal{D}$ is made of pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

@@

\revisions{
	\textit{Scope and Limitations:} A variety of automation applications like packing, stowing, or sorting involve different singulated objects arriving at designated source regions, involving their rearrangement to a disjoint target region or container. Such automation applications also create semi-structured workspaces that guarantee that all objects of interest are easily graspable (top-down for planar surfaces). This class of problems is monotone since the source and target poses are disjoint, and \textit{no transfer will require an intermediate location}. In this case object non-interactivity essentially implies that the workspace is well-behaved enough to allow feasible single-arm motion plans between top-down reachable poses of the object. The current work addresses what we need to do go beyond single arm setups to effectively deploy two arms to speed up such an operation, and theoretically motivates the same.

	The assumptions on the domain laid out in this work serve to identify the class of problems where our theoretical bounds will be close to the attained performance. \textit{The lazy variant proposed in this work is assured to iterate over all possible orderings of object-to-arm assignments, and take into account planning feasibility of the same. As such it is guaranteed to discover a solution as long as the \dual-arm rearrangement problem is monotone.} Admittedly, in domains where these assumptions are pathologically violated the theoretical and practical gains highlighted in this work will be compromised. The proposed method has limiting applicability to some interesting domains where objects are occluded, overlap, or lie in unstructured piles. Any non-monotonicity, i.e. problems that necessitate using an intermediate location, cannot be addressed by the current pipeline. These include puzzle-like or highly cluttered scenarios. 
}

>>>>

\begin{figure}[h]
    % \vspace{-.3in}
	\centering
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    % \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    % \vspace{-.35in}
\end{figure}
Two robot arms \footnote{We shall use superscripts to denote arms, and subscripts to index into some sequence or data-structure dependent on context, unless stated otherwise.} $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of \revisions{$d$-dimensional} Euclidean space $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process. Let the set of collisions induced between the geometries of both the arms at two configurations along the path (at $t$) be denoted by the expression $ \pi^1(t) \ominus \pi^2(t) $. If there are no collisions then $\pi^1(t) \ominus \pi^2(t) = \emptyset$.
% Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. 
The space of dual-arm paths $\mathcal{D}$ is made of pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

@@

\revisions{
	\textit{Scope and Limitations:} A variety of automation applications like packing, stowing, or sorting involve different singulated objects arriving at designated source regions, and require their rearrangement to a disjoint target region or container. Such automation applications also create semi-structured workspaces that guarantee that all objects of interest are easily graspable (top-down for planar surfaces). This class of problems is monotone since the source and target poses are disjoint, and \textit{no transfer will require an intermediate location}. In this case object non-interactivity essentially implies that the workspace is well-behaved enough to allow feasible single-arm motion plans between top-down reachable poses of the object. 
	%The current work addresses what we need to do go beyond single arm setups to effectively deploy two arms to speed up such an operation, and theoretically motivates the same. 
	 The current work addresses what we need to do in order to go beyond single arm setups and in particular in order to effectively deploy two arms to speed up such tasks. Our work also theoretically motivates the use of two arms over a single arm in monotone object rearrangement.

	The assumptions on the domain laid out in this work serve to identify the class of problems where our theoretical bounds will be close to the attained performance. \textit{The lazy variant proposed in this work is assured to iterate over all possible orderings of object-to-arm assignments, and take into account planning feasibility of the same. As such it is guaranteed to discover a solution as long as the \dual-arm rearrangement problem is monotone.} Admittedly, in domains where these assumptions are pathologically violated the theoretical and practical gains highlighted in this work will be compromised. The proposed method has limiting applicability to some interesting domains where objects are occluded, overlap, or lie in unstructured piles. Any non-monotone problems, i.e., problems that necessitate using an intermediate location, cannot be addressed by the current pipeline. These include puzzle-like or highly cluttered scenarios. 
}

### 2020-12-21 08_evaluation.tex
Updates from Overleaf

\revisions{Note that we choose to focus on balanced problem instances where at least half of the objects are reachable to one of the robots. Unbalanced instances can be dealt with using {\tt NO\_ACT} object-to-arm assignments that requires no dual-arm coordination, while the proposed method remains unchanged.}

@@

\revisions{\textit{Note on Heuristic Strategies: } 
	%Alternative simplified strategies exist for this problem domain. A significant complexity in the studied problem arises from the coordination of the arms, especially for general manipulators. Decoupled motion planning here with coordination of single-arm solutions is typically faster but loses guarantees of completeness. 
%	For the assignment of objects to arms fast heuristics can be designed to allocate the objects based some partitioning of the workspace. The focus of the current work is however on problems where the arms have to move and coordinate in common regions where such a partition might not exist, and decoupled solutions might not work.
	 It is possible that instead of the random baseline, some other heuristic might be used to allocate the objects to arms, like the proximity of objects to arms or some workspace partitioning. Such a deterministic, decoupled heuristic will make it faster to compute object-arm assignments than the proposed reasoning, but trade off the optimality bounds posited in this work. Given the object-to-arm assignments feasibility of the solution ultimately depends on coordinated motion planning. It should be noted that committing to a single choice of object assignments seriously affects success rates (especially in the Kuka benchmark). The success is only increased using our proposed lazy approach which takes into account such infeasibility and keeps reattempting other alternatives. A deterministic heuristic however will not offer alternative object-arm assignments and thus is incompatible with the improvements obtained from lazy evaluation. As such we leave the learning and incorporation of appropriate heuristics in this domain as future work and a motivation for practitioners.}

>>>>

\revisions{Note that we choose to focus on balanced problem instances where at least half of the objects are reachable to one of the robots. Unbalanced instances can be dealt with using {\tt NO\_ACT} object-to-arm assignments that require no dual-arm coordination, while the proposed method remains unchanged.}

@@

\revisions{\textit{Note on Heuristic Strategies: } 
	%Alternative simplified strategies exist for this problem domain. A significant complexity in the studied problem arises from the coordination of the arms, especially for general manipulators. Decoupled motion planning here with coordination of single-arm solutions is typically faster but loses guarantees of completeness. 
%	For the assignment of objects to arms fast heuristics can be designed to allocate the objects based some partitioning of the workspace. The focus of the current work is however on problems where the arms have to move and coordinate in common regions where such a partition might not exist, and decoupled solutions might not work.
	 It is possible that instead of the random baseline, some other heuristic might be used to allocate the objects to arms, like the proximity of objects to arms or some workspace partitioning. Such a deterministic, decoupled heuristic will make it faster to compute object-arm assignments than the proposed reasoning, but trade off the optimality bounds posited in this work. Given the object-to-arm assignments feasibility of the solution ultimately depends on coordinated motion planning. It should be noted that committing to a single choice of object assignments seriously affects success rates (especially in the Kuka benchmark). The success is only increased using our proposed lazy approach, which takes into account such infeasibility and keeps reattempting other alternatives. A deterministic heuristic however will not offer alternative object-arm assignments and thus is incompatible with the improvements obtained from lazy evaluation. As such we leave the learning and incorporation of appropriate heuristics in this domain as future work and a motivation for practitioners.}

### 2020-12-21 09_discussion.tex
Updates from Overleaf

\cameraready
{
Work beyond the methods presented in this paper has explored the $k-$arm case. The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions. Effective approximate or lazy solutions to the $k-$arm case can also prove to be power heuristics to the general multi-arm task planning~\cite{shome2019multiarm} challenge. Regrasp reasoning and the use of intermediate locations can extend this work to non-monotone problem instances. The incorporation of manipulation and grasp reasoning with \revisions{real-world object geometries} can also extend such solvers to more cluttered environments. This work serves as a stepping stone in building towards these rich problem domains.
}

>>>>

\cameraready
{
Work beyond the methods presented in this paper has explored the $k$-arm case. The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions. Effective approximate or lazy solutions to the $k$-arm case can also prove to be power heuristics to the general multi-arm task planning~\cite{shome2019multiarm} challenge. Regrasp reasoning and the use of intermediate locations can extend this work to non-monotone problem instances. The incorporation of manipulation and grasp reasoning with \revisions{real-world object geometries} can also extend such solvers to more cluttered environments. This work serves as a stepping stone in building towards these rich problem domains.
}
